%-------------------------
% Resume in Latex
% Author : Sourabh Bajaj
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}

\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
%\addtolength{\oddsidemargin}{-0.375in}
%\addtolength{\evensidemargin}{-0.375in}
%\addtolength{\textwidth}{1in}
%\addtolength{\topmargin}{-.5in}
%\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\Large Amanda Huntington} 
  & Email : amanda.n.huntington@gmail.com \\
  Web: anhuntington.github.io & Mobile : (714) 458-2880 \\
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {California Polytechnic University, San Luis Obispo}{San Luis Obispo, CA}
      {Bachelor of Science in Business Administration}{Sept. 2012 -- June 2016}
      
      {Concentrations: Information Systems, Accounting; }
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
  
  \resumeSubheading
      {Precision Global Consulting}{New York, NY}
      {Senior IT Auditor (Remote Contract)}{Nov 2018 -- Present}
      \resumeItemListStart
      \resumeItem{General}
        {Worked remotely as a consultant for Holtzman Partners, a professional services firm headquartered in Austin, TX as a Senior IT Auditor.}
      \resumeItem{IT Consulting}
      {Participated in a variety of IT consulting projects including internal control design, reviews and model valuations for data-driven software products.}
      \resumeItem{IT Audit}
          {Conducted the testing of IT related controls under various frameworks to determine control effectiveness and to identify areas of control weakness.}
      
      \resumeItemListEnd

    \resumeSubheading
      {Frank, Rimerman + Co. LLP}{San Francisco, CA}
      {Senior Associate, Assurance and Advisory}{Oct 2016 -- Nov 2018}
      \resumeItemListStart
      \resumeItem{General}
        {Gained comprehensive understanding of clients' technical or financial environments, operations, processes, and/or control environments and utilized that knowledge on projects.}
      \resumeItem{Administrative}
      {Participated in information technology and financial audits by assisting in planning, testing and corresponding delegation of duties, report compilation, and project administration}
      \resumeItem{IT Audit}
          {Conducted the testing of IT related controls under various frameworks to determine control effectiveness and to identify areas of control weakness.}
      \resumeItem{Financial Audit}
         {Conducted the testing of various financial audit sections to provide reasonable and sufficient evidence necessary to form an opinion over the financial statements}
       
      \resumeItemListEnd
      
       \resumeSubheading
      {Frank, Rimerman + Co. LLP}{Palo Alto, CA}
      {Accounting Intern}{June 2015 -- Sept 2015}
      \resumeItemListStart
        \resumeItem{Rotational Program}
          {Interned at Frank, Rimerman + Co. LLP the summer of 2015 in the firm's rotational program, which offered the chance to divide time between the departments of assurance, consulting and tax. Internship converted to full-time occupation upon graduation from university.}
      \resumeItemListEnd
      
      \resumeSubheading
      {George G. Ross, CPA}{Morro Bay, CA}
      {Staff Accountant}{Oct. 2013 -- June 2016}
      \resumeItemListStart
        \resumeItem{General}
          {Responsible for general accounting services for a variety of local business clients. Duties included the provision of bookkeeping and related services such as payroll processing.}
        \resumeItem{Tax}
          {Responsible for the preparation of individual and corporate federal and state tax returns, including corresponding coordination with the applicable governing entities.}
        \resumeItem{Nonprofits}
          {Responsible for obtaining and maintaining 501(c)(3) nonprofit status for local charities upon their formation and operation.}
      \resumeItemListEnd

\resumeSubHeadingListEnd
    

%
%--------PROGRAMMING SKILLS------------
\section{Relevant Skills}
  \resumeSubHeadingListStart
  \setlength\itemsep{0em}
   \item{
      \textbf{Languages}{: SQL, \LaTeX, VBA}
   }
   \item {
    \textbf{Frameworks}
          SOC 1, SOC 2, SOX, GAAP, COSO
    }
    
     \item {   \textbf{Technologies}:
          Unix, AWS, Oracle, Salesforce, 
          Relational Databases, Microsoft Excel
     
    }
    \item {
      \textbf{Certifications}: CISA (exam passed Oct. 2018; pending other certification requirements)
    }
  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}

